### 2008-12-17 talk/ecoop2009/intro.tex
add an XXX
steal more text

Moreover, writing a static compiler is often not enough to get high
performances; IronPython and JRuby are going in the direction of JIT compiling
specialized versions of the code depending on the actual values/types seen at
runtime; this approach seems to work, but write it manually requires an
enormous effort.

PyPy's idea is to automatize the generation of static/JIT compilers in order
to reduce at minimun the effort required to get a fast implementation of a
dynamic language; all you have to do is to write a high level specification of
the language (by writing an interpreter), and put it through PyPy's
translation toolchain.

@@

@@

Compilation of the interpreter is implemented as a stepwise
refinement by means of a translation toolchain which performs type
analysis, code optimizations and several transformations aiming at 
incrementally providing implementation details as memory management or the threading model.
The different kinds of intermediate codes  which are refined 
during the translation process are all represented by a collection of control flow graphs,
at several levels of abstractions.

@@

Despite the PyPy infrastructure was specifically developed 
for Python, in fact it can be used for implementing
other languages. Indeed, PyPy has been successfully experimented with
several languages as Smalltalk \cite{BolzEtAl08}, JavaScript, Scheme and Prolog.
As suggested by Figure~\ref{pypy-fig}, a portable interpreter for a
generic language $L$  can be
easily developed once an abstract interpreter for $L$ is implemented in
RPython.

@@

>>>>

Moreover, writing a static compiler is often not enough to get high
performance; IronPython and JRuby are going in the direction of JIT compiling
specialized versions of the code depending on the actual values/types seen at
runtime; this approach seems to work, but writing it manually requires an
enormous effort.

\cfbolz{we should cite the dyla paper somewhere here}

PyPy's idea is to automatize the generation of JIT compilers in order
to reduce to a minimum the effort required to get a fast implementation of a
dynamic language; all you have to do is to write a high level specification of
the language (by writing an interpreter), and putting it through PyPy's
translation toolchain. The automatic generation of JIT compilers is done with
the help of partial evaluation techniques.

@@

\anto{as Armin points out, the two CLI backends can be easily confused; what
  about renaming the ``CLI Backend for flowgraphs'' into ``CLI bytecode
  compiler''? Any better idea for the name?}

@@

Compilation of the interpreter is implemented as a stepwise
refinement by means of a translation toolchain which performs type
analysis, code optimizations and several transformations aiming at 
incrementally providing implementation details such as memory management or the threading model.
The different kinds of intermediate codes  which are refined 
during the translation process are all represented by a collection of control flow graphs,
at several levels of abstractions.

@@

Despite having been specifically developed for Python, the PyPy infrastructure
can in fact be used for implementing other languages. Indeed, there were
successful experiments of using PyPy to implement several other languages such
as Smalltalk \cite{BolzEtAl08}, JavaScript, Scheme and Prolog.
As suggested by Figure~\ref{pypy-fig}, a portable interpreter for a
generic language $L$  can be
easily developed once an interpreter for $L$ has been implemented in
RPython.

\subsection{PyPy and JIT-Generation}

This section will give a high-level overview of how the JIT-generation process
works. More details will be given in subsequent sections.

@@

XXX list contributions clearly
